Concave reduction in Self-Healing Swarms

### 2018-11-15 paper.tex
last maths woven in

\begin{equation}
\label{eq:SwarmStabilityDistance1}
\mu_d(b) =
\frac{1}{\mathlarger{\card{\mathcal{N}_b}}}\left({\mathlarger{\sum_{b' \in
\mathcal{N}_b}}\magn{bb'}}\right)
\end{equation}

@@

\begin{equation}
\label{eq:SwarmStabilityDistance2}
\mu_d(\mathcal{S}) = \frac{\mathlarger{\sum_{b \in
\mathcal{S}}}~\mathlarger{\sum_{b' \in
\mathcal{N}_b}}\magn{bb'}}{\mathlarger{\sum_{b \in
\mathcal{S}}\card{\mathcal{N}_b}}}
\end{equation}

@@

\begin{equation}
\label{eq:SwarmStabilityDistance3}
\sigma_d(\mathcal{S}) = \sqrt{\frac{\mathlarger{\sum_{b \in
\mathcal{S}}}~\mathlarger{\sum_{b' \in \mathcal{N}_b}}\Big(\magn{bb'} -
\mu_d(\mathcal{S})\Big)^2}{\mathlarger{\sum_{b \in
\mathcal{S}}\card{\mathcal{N}_b}}}}
\end{equation}

The distance-based metric for the internal distribution of the agents is therefore $\mu_d(\mathcal{S})$ and $\sigma_d(\mathcal{S})$. This can be written informally as:

\begin{equation}
\label{eq:SwarmDistanceMetric}
\psi_d(\mathcal{S}) = \mu_d(\mathcal{S})\pm \sigma_d(\mathcal{S})
\end{equation}

@@

\begin{equation}
\label{eq:CohesionRepulsion}
P(b) = \left\{\begin{array}{lll}
               |v(b)|& \mathrm{if} & |k_cv_c(b)| > |k_r v_r(b)|\\
              -|v(b)|& \mathrm{otherwise}
              \end{array}\right.
\end{equation}

Although it is possible for $v(b)$ to be null there could still be variation in the constituent components. The variation calculation (standard deviation) as shown in Equation~\ref{eq:SwarmStabilityQuotientT}.

@@

\begin{equation}
\label{eq:SwarmStabilityMetricT3}
\mu_p(\mathcal{S}) = \frac{\mathlarger{\sum_{b \in \mathcal{S}} P(b)}}{\mathlarger{\sum_{b \in \mathcal{S}}}|\mathcal{N}_b| + \mathlarger{\sum_{b \in \mathcal{S}}}|rep(b)|}
\end{equation}
\fbox{\textit{what is $rep(b)$ here ?}}
The standard deviation associated with this mean is calculated as Equation~\ref{eq:SwarmStabilityQuotientT}.

\begin{equation}
\label{eq:SwarmStabilityQuotientT}
\sigma_p(\mathcal{S}) = \sqrt{\frac{\mathlarger{\sum_{b \in \mathcal{S}}}\Big(P(b)-\mu_p(\mathcal{S})\Big)^2}{\mathlarger{\sum_{b \in \mathcal{S}}}|\mathcal{N}_b| + \mathlarger{\sum_{b \in \mathcal{S}}}|rep(b)|}}
\end{equation}

The metric for the internal movement is this pair of numbers, the mean and standard deviation of the swarm's internal \textit{cohesion/repulsion}. The pair $\mu_p(\mathcal{S})$, $\sigma_p(\mathcal{S})$ may be written informally as:

\begin{equation}
\label{eq:SwarmPotentialMagnitude}
\psi_p(\mathcal{S}) = \mu_p(\mathcal{S})\pm \sigma_p(\mathcal{S})
\end{equation}

>>>>

\begin{equation}
\label{eq:SwarmStabilityDistance1}
\mu_d(b) =
\frac{1}{\mathlarger{\card{\mathcal{N}_b}}}\left({\mathlarger{\sum_{b' \in
\mathcal{N}_b}}\magn{\vec b'}}\right)
\end{equation}

@@

\begin{equation}
\label{eq:SwarmStabilityDistance2}
\mu_d(\mathcal S) = \frac{\mathlarger{\sum_{b \in
\mathcal S}}~\mathlarger{\sum_{b' \in
\mathcal{N}_b}}\magn{\vec b'}}{\mathlarger{\sum_{b \in
\mathcal S}\card{\mathcal{N}_b}}}
\end{equation}
\fbox{is this an over estimate -- distances are counted twice}

@@

\begin{equation}
\label{eq:SwarmStabilityDistance3}
\sigma_d(\mathcal S) = \sqrt{\frac{\mathlarger{\sum_{b \in
\mathcal S}}~\mathlarger{\sum_{b' \in \mathcal{N}_b}}\Big(\magn{\vec b'} -
\mu_d(\mathcal S)\Big)^2}{\mathlarger{\sum_{b \in
\mathcal S}\card{\mathcal{N}_b}}}}
\end{equation}

The distance-based metric for the internal distribution of the agents is therefore $\mu_d(\mathcal S)$ and $\sigma_d(\mathcal S)$. This can be written informally as:

\begin{equation}
\label{eq:SwarmDistanceMetric}
\psi_d(\mathcal S) = \mu_d(\mathcal S)\pm \sigma_d(\mathcal S)
\end{equation}

@@

\begin{equation}
\label{eq:CohesionRepulsion}
P(b) = \left\{\begin{array}{lll}
               |\vec v(b)|& \mathrm{if} & |k_c \vec v_c(b)| > |k_r \vec v_r(b)|\\
              -|\vec v(b)|& \mathrm{otherwise}
              \end{array}\right.
\end{equation}

Although it is possible for $\vec v(b)$ to be null there could still be variation in the constituent components. The variation calculation (standard deviation) as shown in Equation~\ref{eq:SwarmStabilityQuotientT}.

@@

\begin{equation}
\label{eq:SwarmStabilityMetricT3}
\mu_p(\mathcal S) = \frac{\mathlarger{\sum_{b \in \mathcal S} P(b)}}{\mathlarger{\sum_{b \in \mathcal S}}|\mathcal{N}_b| + \mathlarger{\sum_{b \in \mathcal S}}|\mathcal R_b|}
\end{equation}
Where $\mathcal R_b$ is the set of neighbours subject to repulsion, 
where $\mathcal R_b \subseteq \mathcal N_b$ and $\vec b'\in\mathcal R_b:\magn{\vec b'}\leq R_b$
The standard deviation associated with this mean is calculated as Equation~\ref{eq:SwarmStabilityQuotientT}.

\begin{equation}
\label{eq:SwarmStabilityQuotientT}
\sigma_p(\mathcal S) = \sqrt{\frac{\mathlarger{\sum_{b \in \mathcal S}}\Big(P(b)-\mu_p(\mathcal S)\Big)^2}{\mathlarger{\sum_{b \in \mathcal S}}|\mathcal{N}_b| + \mathlarger{\sum_{b \in \mathcal S}}|\mathcal R_b|}}
\end{equation}

The metric for the internal movement is this pair of numbers, the mean and standard deviation of the swarm's internal \textit{cohesion/repulsion}. The pair $\mu_p(\mathcal S)$, $\sigma_p(\mathcal S)$ may be written informally as:

\begin{equation}
\label{eq:SwarmPotentialMagnitude}
\psi_p(\mathcal S) = \mu_p(\mathcal S)\pm \sigma_p(\mathcal S)
\end{equation}
